Stellar Migration and Chemical Enrichment in the Milky Way Disc: A Hybrid Model

### 2021-09-17 chemev/MWbimodality/paper/draft3/methods.tex
final paper updates

implied final radius at~$T$ = 13.2 Gyr with an assumed time dependence (see 
below). 

@@

database \citep{Cristallo2011}. 

@@

	\item \textbf{Inside-Out}: This is our fiducial SFH, 
	\begin{equation} 
	f_\text{IO}(t|\rgal) = (1 - e^{-t / \tau_\text{rise}}) 
	e^{-t / \tau_\text{sfh}}. 
	\label{eq:insideout_sfh} 
	\end{equation} 
	We adopt this mathematical form over the somewhat more common 
	$te^{-t/\tau_\text{sfh}}$ because it allows separate control over the 
	rising and falling phase of the SFH. 
	Equation~\refp{eq:insideout_sfh} has a maximum near~$\tau_\text{rise}$, 
	which in this paper we set to 2 Gyr at all radii. 
	This form produces a peak in star formation at lookback times of~$\sim$11 
	Gyr, roughly corresponding to a redsfhit of~$z \approx$ 2.5. 
	{\color{red} 
	In detail, however, the time of peak star formation increases 
	with~$\tau_\text{sfh}$, which in turn increases with~\rgal~in our models 
	(see discussion below). 
	As a result,~$\dot{\Sigma}_\star$ in the outer disc instead reaches its 
	peak at lookback times of~$\sim$7 - 8 Gyr, qualitatively consistent with 
	the radial growth of the Galaxy~\citep[e.g.][]{Bird2012, Bird2013}. 
	} 
	% We discuss the choice of~$\tau_\text{sfh}$ below.

@@

The inside-out model is our fiducial choice, and it is the model shown in 
figures unless otherwise specified. 
The constant SFR model allows us to investigate the impact of migration when 
the time-dependence of the SFH is removed, and the two burst models allow us to 
explore the consequences of elevated recent star formation supported by some 
recent data. 
{\color{red} 
More complex scenarios, such as multiple bursts induced by repeated satellite 
passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} or 
the onset of star formation occurring later in the outer disc to better capture 
the radial growth of the Galaxy~\citep[e.g.][]{Bird2012, Bird2013}, can be 
explored easily using~\vice, but we do not explore such models here. 
} 
% More complex scenarios with multiple bursts induced by repeated satellite 
% passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} 
% can be modeled easily in~\vice, but we do not explore them here. 
\par 
We derive the~$\tau_\text{sfh}-\rgal$ relation from the data of 
\citet{Sanchez2020}, who presents the stellar surface density~$\Sigma_\star$ as 
a function of age in bins of~$R/R_\text{e}$ for MaNGA 
galaxies~\citep{Bundy2015}, where $R_\text{e}$ is the half-light radius. 
Here we take the~$M_\star = 10^{10.5} - 10^{11}~\msun$~bin for Sa/Sb spirals 
and simultaneously fit the normalization and e-folding timescale 
$\tau_\text{sfh}$ of our~$f_\text{IO}(t|\rgal)$ form to the data. 
Although the normalization is irrelevant to our models and determined via the 
method outlined in Appendix~\ref{sec:normalize_sfh}, we adopt the resulting 
$\tau_\text{sfh}-\rgal$ relation in our models. 
Our adopted stellar surface density gradient 
(see~\S~\ref{sec:methods:surface_density_gradient}) implies a present-day 
half-mass radius near 4 kpc. 
The findings of~\citet{Garcia-Benito2017} and~\citet{GonzalezDelgado2014} 
suggest that half-light radii are marginally larger than half-mass radii. 
Based on equation (4) of~\citet{GonzalezDelgado2014} relating the two for 
circular apertures, we expect our model Galaxy to have a 
half-light radius near 5 kpc. 
We therefore adopt~$R_\text{e}$ = 5 kpc to convert the 
$\tau_\text{sfh}-\rgal/R_\text{e}$ relation resulting from our fit to the 
\citet{Sanchez2020} data into a~$\tau_\text{sfh}-\rgal$ relation. 
\par 
We illustrate this relationship in the bottom panel of Fig. 
\ref{fig:eta_tau_sfh}. 
The resulting timescales are long, particularly for the outer Galaxy. 
With a red dotted line, we highlight a value of~$\tau_\text{sfh} \approx$~15 
Gyr at an assumed orbital radius of the sun of $R_\odot$ = 8 kpc. 
The long timescales reflect the fact that the 
$\Sigma_\star(\tau_\text{lookback})$ profiles in Fig. 11 of~\citet{Sanchez2020} 
are fairly flat. 
For comparison, we have also considered the assumption that the Galactic SFH 
may have resembled the cosmic SFH by running models with e-folding timescales 
of a~$\sim$few Gyr~\citep[e.g.][]{Madau2014}. 
We find similar results in these cases, suggesting that our qualitative 
conclusions are not sensitive to the exact values of~$\tau_\text{sfh}$.

@@

\begin{table*} 
% \color{red} 
\caption{
A summary of our chemical evolution model parameters, their fiducial values, 
and in what section of the text relevant discussion can be found. 
}
\begin{tabularx}{\textwidth}{l @{\extracolsep{\fill}} l l r} 
\hline 
\hline 
Quantity & Section & Description & Fiducial Value(s) 
\\ 
\hline 
\rgal & N/A & Galactocentric Radius & $0 - 20$ kpc 
\\ 
$\delta$\rgal & \ref{sec:methods:summary} & Width of each concentric ring & 
100 pc 
\\ 
$\Delta$\rgal & \ref{sec:methods:migration} & Change in orbital radius due to 
stellar migration; adopted from~\hsim~analogue star particle & N/A 
\\ 
$z$ & \ref{sec:methods:migration} & Present day distance to Galactic midplane; 
adopted from~\hsim~analogue star particle & $-3 - +3$ kpc 
\\ 
$T_\text{max}$ & \ref{sec:methods:h277} & Time interval over which our models 
are integrated & 13.2 Gyr 
\\ 
$\delta T$ & \ref{sec:methods:summary} & Timestep size & 10 Myr 
\\ 
$n$ & \ref{sec:methods:summary} & Number of stellar populations formed per ring 
per timestep & 8 
\\ 
$R_\text{SF}$  & \ref{sec:methods:summary} & Maximum radius of star formation 
(i.e.~$\dot{\Sigma}_\star$ = 0 at~\rgal~>~$R_\text{SF}$) & 15.5 kpc 
\\ 
$\tau_\star$ & \ref{sec:methods:sfe} & The SFE timescale of the ISM: 
$\tau_\star \equiv \Sigma_\text{gas} / \dot{\Sigma}_\star$ & N/A 
\\ 
$\tau_{\text{mol},0}$ & \ref{sec:methods:sfe} & The SFE timescale of molecular 
hydrogen at the present day & 2 Gyr 
\\ 
$\gamma$ & \ref{sec:methods:sfe} & The power-law index describing the 
time-dependence of the molecular hydrogen SFE timescale 
(i.e.~$\tau_\text{mol}\sim t^\gamma$) & 1/2 
\\ 
$\eta$ & \ref{sec:methods:outflows} & The outflow mass-loading factor: 
$\eta \equiv \dot{\Sigma}_\text{out}/\dot{\Sigma}_\star$ (assumed to be 
time-independent) & equation~\refp{eq:eta_rgal} 
\\ 
$y_\text{O}^\text{CC}$ & \ref{sec:methods:yields} & CCSN yield of O & 0.015 
\\ 
$y_\text{Fe}^\text{CC}$ & \ref{sec:methods:yields} & CCSN yield of Fe & 0.0012 
\\ 
$y_\text{O}^\text{Ia}$ & \ref{sec:methods:yields} & SN Ia yield of O & 0 
\\ 
$y_\text{Fe}^\text{Ia}$ & \ref{sec:methods:yields} & SN Ia yield of Fe & 0.00214 
\\ 
$\dot{\Sigma}_\star$ & \ref{sec:methods:sfhs} & Surface density of star 
formation & N/A
\\ 
$f_\text{IO}(t|\rgal)$ & \ref{sec:methods:sfhs} & The time-dependence of the 
star formation history in the inside-out model & 
equation~\refp{eq:insideout_sfh} 
\\ 
$f_\text{LB}(t|\rgal)$ & \ref{sec:methods:sfhs} & The time-dependence of the 
star formation history in the late-burst model & 
equation~\refp{eq:lateburst_sfh} 
\\ 
\hline 
\end{tabularx} 
\label{tab:params} 
\end{table*}

@@

We plot the resultant surface density gradients from our fiducial, inside-out 
SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
stellar gradient and the gas in blue. 
The stellar gradient very nearly follows our target gradient (equation 
\ref{eq:gradient}) denoted by the solid black line. 
{\color{red} 
Simply introducing scatter around the adopted trend, stellar migration has 
not significantly altered the overall form of the gradient, as we assumed in 
Appendix~\ref{sec:normalize_sfh}; we find this to also be true for our sample 
of star particles from~\hsim. 
}
% Stellar migration has not altered the overall form of the gradient, simply 
% introducing scatter around the adopted trend. 
Although there are slight enhancements at small~$\rgal$ and deficits at large 
$\rgal$, the agreement is excellent in the regions of the Galaxy where the 
gradient is best constrained observationally. 
The~$\rgal$ > 15.5 kpc populations are composed entirely of stars that 
migrated there, since that is the radius at which we shut off star formation. 
The gas gradient shows a break in the scale radius near~$\rgal \approx$ 
6 kpc. This is a consequence of our adopted star formation law; at 
$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). 
\par 
Although we adopt the~\citet{Licquia2015} disc stellar mass of the Milky Way 
here, we find similar results when taking a value which differs even by an 
order of magnitude. 
If we used a linear star formation law, then our chemical evolution would be 
independent of the mass normalization as it is in corresponding one-zone 
models (\citealp*{Spitoni2017};~\citealp{Weinberg2017, Belfiore2019}). 
The mass normalization enters our calculation because it affects the transition 
between the linear and non-linear regimes of our star formation law 
(equation~\ref{eq:sf_law}), but the impact on abundance evolution is minimal.

>>>>

implied final radius and~$z$ at~$T$ = 13.2 Gyr with an assumed time dependence 
(see below). 

@@

database~\citep{Cristallo2011, Cristallo2015}. 

@@

	\item \textbf{Inside-Out}: This is our fiducial SFH, 
	\begin{equation} 
	f_\text{IO}(t|\rgal) = (1 - e^{-t / \tau_\text{rise}}) 
	e^{-t / \tau_\text{sfh}}. 
	\label{eq:insideout_sfh} 
	\end{equation} 
	We adopt this mathematical form over the somewhat more common 
	$te^{-t/\tau_\text{sfh}}$ because it allows separate control over the 
	rising and falling phase of the SFH. 
	Equation~\refp{eq:insideout_sfh} has a maximum near~$\tau_\text{rise}$, 
	which in this paper we set to 2 Gyr at all radii. 
	This form produces a peak in star formation at lookback times of~$\sim$11 
	Gyr, roughly corresponding to a redsfhit of~$z \approx$ 2.5. 
	{\color{red} 
	In detail, however, the time of peak star formation increases 
	with~$\tau_\text{sfh}$, which in turn increases with~\rgal~in our models 
	(see discussion below). 
	As a result,~$\dot{\Sigma}_\star$ in the outer disc instead reaches its 
	peak at lookback times of~$\sim$7 - 8 Gyr, qualitatively consistent with 
	the radial growth of disc galaxies~\citep{Bird2013, Bird2021, Frankel2019}. 
	} 
	% We discuss the choice of~$\tau_\text{sfh}$ below.

@@

The inside-out model is our fiducial choice, and it is the model shown in 
figures unless otherwise specified. 
The constant SFR model allows us to investigate the impact of migration when 
the time-dependence of the SFH is removed, and the two burst models allow us to 
explore the consequences of elevated recent star formation supported by some 
recent data. 
{\color{red} 
More complex scenarios, such as multiple bursts induced by repeated satellite 
passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} or 
the onset of star formation occurring later in the outer disc to better capture 
the radial growth of the Galaxy~\citep[e.g.][]{Frankel2019}, can be 
explored easily using~\vice, but we do not explore such models here. 
} 
% More complex scenarios with multiple bursts induced by repeated satellite 
% passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} 
% can be modeled easily in~\vice, but we do not explore them here. 
\par 
We derive the~$\tau_\text{sfh}-\rgal$ relation from the data of 
\citet{Sanchez2020}, who presents the stellar surface density~$\Sigma_\star$ as 
a function of age in bins of~$R/R_\text{e}$ for MaNGA 
galaxies~\citep{Bundy2015}, where $R_\text{e}$ is the half-light radius. 
Here we take the~$M_\star = 10^{10.5} - 10^{11}~\msun$~bin for Sa/Sb spirals 
and simultaneously fit the normalization and e-folding timescale 
$\tau_\text{sfh}$ of our~$f_\text{IO}(t|\rgal)$ form to the data. 
Although the normalization is irrelevant to our models and determined via the 
method outlined in Appendix~\ref{sec:normalize_sfh}, we adopt the resulting 
$\tau_\text{sfh}-\rgal$ relation in our models. 
Our adopted stellar surface density gradient 
(see~\S~\ref{sec:methods:surface_density_gradient}) implies a present-day 
half-mass radius near 4 kpc. 
The findings of~\citet{Garcia-Benito2017} and~\citet{GonzalezDelgado2014} 
suggest that half-light radii are marginally larger than half-mass radii. 
Based on equation (4) of~\citet{GonzalezDelgado2014} relating the two for 
circular apertures, we expect our model Galaxy to have a 
half-light radius near 5 kpc. 
We therefore adopt~$R_\text{e}$ = 5 kpc to convert the 
$\tau_\text{sfh}-\rgal/R_\text{e}$ relation resulting from our fit to the 
\citet{Sanchez2020} data into a~$\tau_\text{sfh}-\rgal$ relation. 
\par 
We illustrate this relationship in the bottom panel of Fig. 
\ref{fig:eta_tau_sfh}. 
The resulting timescales are long, particularly for the outer Galaxy. 
With a red dotted line, we highlight a value of~$\tau_\text{sfh} \approx$~15 
Gyr at an assumed orbital radius of the sun of $R_\odot$ = 8 kpc. 
The long timescales reflect the fact that the 
$\Sigma_\star(\tau_\text{lookback})$ profiles in Fig. 11 of~\citet{Sanchez2020} 
are fairly flat. 
For comparison, we have also considered the assumption that the Galactic SFH 
may have resembled the cosmic SFH by running models with e-folding timescales 
of a~$\sim$few Gyr~\citep[e.g.][]{Madau2014}. 
We find similar results in these cases, suggesting that our qualitative 
conclusions are not sensitive to the exact values of~$\tau_\text{sfh}$.

@@

\begin{table*} 
% \color{red} 
\caption{
A summary of our chemical evolution model parameters, their fiducial values, 
and in what section of the text relevant discussion can be found. 
}
\begin{tabularx}{\textwidth}{l @{\extracolsep{\fill}} l l r} 
\hline 
\hline 
Quantity & Section & Description & Fiducial Value(s) 
\\ 
\hline 
\rgal & N/A & Galactocentric Radius & $0 - 20$ kpc 
\\ 
$\delta$\rgal & \ref{sec:methods:summary} & Width of each concentric ring & 
100 pc 
\\ 
$\Delta$\rgal & \ref{sec:methods:migration} & Change in orbital radius due to 
stellar migration; adopted from~\hsim~analogue star particle & N/A 
\\ 
$z$ & \ref{sec:methods:migration} & Present day distance to Galactic midplane; 
adopted from~\hsim~analogue star particle & [$-3$, 3] kpc 
\\ 
$T_\text{max}$ & \ref{sec:methods:h277} & Time interval over which our models 
are integrated & 13.2 Gyr 
\\ 
$\delta T$ & \ref{sec:methods:summary} & Timestep size & 10 Myr 
\\ 
$n$ & \ref{sec:methods:summary} & Number of stellar populations formed per ring 
per timestep & 8 
\\ 
$R_\text{SF}$  & \ref{sec:methods:summary} & Maximum radius of star formation 
(i.e.~$\dot{\Sigma}_\star$ = 0 at~\rgal~>~$R_\text{SF}$) & 15.5 kpc 
\\ 
$\tau_\star$ & \ref{sec:methods:sfe} & The SFE timescale of the ISM: 
$\tau_\star \equiv \Sigma_\text{gas} / \dot{\Sigma}_\star$ & N/A 
\\ 
$\tau_{\text{mol},0}$ & \ref{sec:methods:sfe} & The SFE timescale of molecular 
hydrogen at the present day & 2 Gyr 
\\ 
$\gamma$ & \ref{sec:methods:sfe} & The power-law index describing the 
time-dependence of the molecular hydrogen SFE timescale 
(i.e.~$\tau_\text{mol}\sim t^\gamma$) & 1/2 
\\ 
$\eta$ & \ref{sec:methods:outflows} & The outflow mass-loading factor: 
$\eta \equiv \dot{\Sigma}_\text{out}/\dot{\Sigma}_\star$ (assumed to be 
time-independent) & equation~\refp{eq:eta_rgal} 
\\ 
$y_\text{O}^\text{CC}$ & \ref{sec:methods:yields} & CCSN yield of O & 0.015 
\\ 
$y_\text{Fe}^\text{CC}$ & \ref{sec:methods:yields} & CCSN yield of Fe & 0.0012 
\\ 
$y_\text{O}^\text{Ia}$ & \ref{sec:methods:yields} & SN Ia yield of O & 0 
\\ 
$y_\text{Fe}^\text{Ia}$ & \ref{sec:methods:yields} & SN Ia yield of Fe & 0.00214 
\\ 
$\dot{\Sigma}_\star$ & \ref{sec:methods:sfhs} & Surface density of star 
formation & N/A
\\ 
$f_\text{IO}(t|\rgal)$ & \ref{sec:methods:sfhs} & The time-dependence of the 
star formation history in the inside-out model & 
equation~\refp{eq:insideout_sfh} 
\\ 
$f_\text{LB}(t|\rgal)$ & \ref{sec:methods:sfhs} & The time-dependence of the 
star formation history in the late-burst model & 
equation~\refp{eq:lateburst_sfh} 
\\ 
\hline 
\end{tabularx} 
\label{tab:params} 
\end{table*}

@@

We plot the resultant surface density gradients from our fiducial, inside-out 
SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
stellar gradient and the gas in blue. 
The stellar gradient very nearly follows our target gradient (equation 
\ref{eq:gradient}) denoted by the solid black line. 
{\color{red} 
Simply introducing scatter around the adopted trend, stellar migration has 
not significantly altered the overall form of the gradient, as we assumed in 
Appendix~\ref{sec:normalize_sfh}. 
We find this to also be true for our sample of star particles from~\hsim, 
a result which is expected given the roughly symmetric shapes of the 
histograms in the top row of Fig.~\ref{fig:h277_decomposition} and consistent 
with previous arguments that radial migration does not significantly alter the 
vertical and radial structure of the disc~\citep[e.g.][]{Sellwood2014, 
VeraCiro2014}. 
}
% Stellar migration has not altered the overall form of the gradient, simply 
% introducing scatter around the adopted trend. 
Although there are slight enhancements at small~$\rgal$ and deficits at large 
$\rgal$, the agreement is excellent in the regions of the Galaxy where the 
gradient is best constrained observationally. 
The~$\rgal$ > 15.5 kpc populations are composed entirely of stars that 
migrated there, since that is the radius at which we shut off star formation. 
The gas gradient shows a break in the scale radius near~$\rgal \approx$ 
6 kpc. This is a consequence of our adopted star formation law; at 
$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). 
\par 
Although we adopt the~\citet{Licquia2015} disc stellar mass of the Milky Way 
here, we find similar results when taking a value which differs even by an 
order of magnitude. 
If we used a linear star formation law, then our chemical evolution would be 
independent of the mass normalization as it is in corresponding one-zone 
models (\citealp*{Spitoni2017};~\citealp{Weinberg2017, Belfiore2019}). 
The mass normalization enters our calculation because it affects the transition 
between the linear and non-linear regimes of our star formation law 
(equation~\ref{eq:sf_law}), but the impact on abundance evolution is minimal.

### 2021-09-17 chemev/MWbimodality/paper/draft3/vice.tex
final paper updates

\vice~is an open-source~\texttt{python} package available for Linux and Mac OS 
X.\footnote{ 
	Install (PyPI): \url{https://pypi.org/project/vice} \\ 
	Documentation: \url{https://vice-astro.readthedocs.io} \\ 
	Source Code: \url{https://github.com/giganano/VICE.git} 
} 
Windows users should install and use~\vice~entirely within the Windows Subsystem 
for Linux. 
It requires~\texttt{python >=}~3.6 and can be installed in a terminal via 
\texttt{pip install vice}, after which~\texttt{vice -{}-docs} will launch a web 
browser to the documentation at \url{https://vice-astro.readthedocs.io}. 
\texttt{vice -{}-tutorial} will also 
launch a web browser, but to a jupyter notebook in the GitHub repository 
intended to familiarize first-time users with~\vice's API. 
\texttt{Python} code that runs the simulations presented in this paper is 
included as supplementary material in the GitHub repository; they can be run 
from a terminal without modifying the source code. 
When taking into account time-dependent stellar migration,~\vice~requires 
$\sim$2.5 CPU-hours per chemical element to compute masses, abundances, and 
initial and final Galactic regions for~$\sim$1.6 million stellar populations 
spanning a little over 1,300 timesteps. 
This estimate was made using a single core with a 3 GHz processor. 
Although their outputs require only~$\sim$235 MB of disc space each, our models 
as computed in this paper can require up to~$\sim$3 GB of RAM at any given 
time owing to the number of timesteps and stellar populations used, but these 
can be adjusted via command line arguments. 
Beyond what has been presented in this paper,~\vice's capabilities include 
user-defined, arbitrary functions of time describing star formation and infall 
histories, star formation laws, outflow prescriptions, SN Ia delay-time 
distributions, and element-by-element infall metallicities. 
It allows the IMF to be a user-defined function of stellar mass. 
It will compute yields from supernova and asymptotic giant branch star 
nucleosynthesis studies, but allows the user to specify arbitrary mathematical 
forms for use in chemical evolution models. 
A complete breakdown of its abilities can be found in the documentation. 
While providing this level of versatility in a~\texttt{python} package, 
\vice~also enjoys a backend implemented in ANSI/ISO~\texttt{C}, providing it 
with the powerful computing speeds of a compiled library; with typical 
parameters, yield calculations and one-zone model integrations require only a 
fraction of a second.

>>>>

\vice~is an open-source~\texttt{python} package available for Linux and Mac OS 
X.\footnote{ 
	Install (PyPI): \url{https://pypi.org/project/vice} \\ 
	Documentation: \url{https://vice-astro.readthedocs.io} \\ 
	Source Code: \url{https://github.com/giganano/VICE.git} 
} 
Windows users should install and use~\vice~entirely within the Windows Subsystem 
for Linux. 
The latest version (1.2.1) requires~\texttt{python >=}~3.6 and can be 
installed in a terminal via~\texttt{pip install vice}, after 
which~\texttt{vice -{}-docs} will launch a web browser to the documentation 
at~\url{https://vice-astro.readthedocs.io}. 
\texttt{vice -{}-tutorial} will also 
launch a web browser, but to a jupyter notebook in the GitHub repository 
intended to familiarize first-time users with~\vice's API. 
\texttt{Python} code that runs the simulations presented in this paper is 
included as supplementary material in the GitHub repository; they can be run 
from a terminal without modifying the source code. 
When taking into account time-dependent stellar migration,~\vice~requires 
$\sim$2.5 CPU-hours per chemical element to compute masses, abundances, and 
initial and final Galactic regions for~$\sim$1.6 million stellar populations 
spanning a little over 1,300 timesteps. 
This estimate was made using a single core with a 3 GHz processor. 
Although their outputs require only~$\sim$235 MB of disc space each, our models 
as computed in this paper can require up to~$\sim$3 GB of RAM at any given 
time owing to the number of timesteps and stellar populations used, but these 
can be adjusted via command line arguments. 
Beyond what has been presented in this paper,~\vice's capabilities include 
user-defined, arbitrary functions of time describing star formation and infall 
histories, star formation laws, outflow prescriptions, SN Ia delay-time 
distributions, and element-by-element infall metallicities. 
It allows the IMF to be a user-defined function of stellar mass. 
It will compute yields from supernova and asymptotic giant branch star 
nucleosynthesis studies, but allows the user to specify arbitrary mathematical 
forms for use in chemical evolution models. 
A complete breakdown of its abilities can be found in the documentation. 
While providing this level of versatility in a~\texttt{python} package, 
\vice~also enjoys a backend implemented in ANSI/ISO~\texttt{C}, providing it 
with the powerful computing speeds of a compiled library; with typical 
parameters, yield calculations and one-zone model integrations require only a 
fraction of a second.
